A Study on Penguins: A Minimal Reproducible Example

### 2024-08-23 01_Example/Manuscript.qmd
Make Welch t-test explicit

# Perform t-test
t_test_result <- t.test(bill_length_mm ~ sex, data = dat_clean)

@@

We conducted a two-sample t-test to compare the average bill lengths between male and female penguins.
The null hypothesis ($H_0$) states that there is no difference in bill lengths between male and female penguins, while the alternative hypothesis ($H_1$) suggests a significant difference.

>>>>

# Perform t-test
t_test_result <- t.test(bill_length_mm ~ sex, data = dat_clean, var.equal = FALSE)

@@

We conducted a two-sample Welch t-test to compare the average bill lengths between male and female penguins.
The null hypothesis ($H_0$) states that there is no difference in bill lengths between male and female penguins, while the alternative hypothesis ($H_1$) suggests a significant difference.
